\textls[-0]{\thetitle}

### 2023-03-23 metatheory-condensed.tex
bugfixes

In rules \ruleref{l/add} and \ruleref{lsig/add},
the third premise $\goodTerm{\Gm,x : \TyTkg{\lsig}}{\seal}{A}$ is
responsible for hiding W-type signatures.
Here, $\TyTkg{\lsig}$ packages $\lsig$---recall that $\lsig$ contains the
(self-parameterized) types of all the fields preceding the current
field~$t$---into a dependent tuple type (\ruleref{tyeq/pk/add}).
The term $\seal$ turns a tuple of type $\TyTkg{\lsig}$ into a new tuple of type~$A$
that hides W-type signatures behind $\cU$, if necessary.
%
It is straightforward to find the~$\seal$ that fits the bill, though this process
is not automated in \TT.
In particular, when no hiding is needed, $\seal$ is simply~$x$,
%\EDJ{$\var{0}$ is not identity (substitution), but the first variable, right? Or you meant to say it is identity ``sealing''?}\YZreply{Yes, I meant identity sealing. I cannot say 'sealing' because the paper currently does not use the word sealing anywhere.}\EDJreply{What about just remove the parenthesis and ``the identity''}
and $A$ is $\TyTkg{\lsig}$.
In \cref{fig:stlc-linkage-typing}, $\seal_1$, $\seal_2$, and $\seal_{10}$ are simply $x$,
and $\seal_6$ has the typing
\begingroup
\fontsize{9}{9}\selectfont%
\goodTerm{
  \mathit{self} :
  \big[\texttt{tm} : \TyS{\wcode{\wsig_{\texttt{tm}}}},\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
}{
  \seal_6
}{
  \big[\texttt{tm} : \cU,\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
}.
\endgroup

@@

Derived families can be modeled as linkage transformers inductively
constructed from the introduction forms
$\small\InhId$, $\small\InhExt{h}{x.t}$, $\small\InhOv{h}{x.t}$, $\small\InhInh{h}$, etc.
\cref{fig:fmltt-selected} shows the $\beta$-rule of an exemplary transformer,
\ruleref{tmeq/ov/beta}.
It states that applying the transformer $\small\InhOv{h}{\mathit{self}_2.t_2}$ to
a linkage of form $\LkgAdd{\lkg}{\mathit{self}_1.t_1}$
overrides the linkage's last field~$t_1$ with~$t_2$.
For instance, the construction below shows that 
$\small\InhOv{\InhId}{\wcode{\wsig'_{\texttt{tm}}}}$
is used as the first step in creating a linkage transformer modeling a derived family that
overrides $\wsig_{\texttt{tm}}$ with an extended
signature~$\wsig'_{\texttt{tm}}$:
\vspace{.9ex}

>>>>

In rules \ruleref{l/add} and \ruleref{lsig/add},
the third premise $\goodTerm{\Gm,x : \TyTkg{\lsig}}{\seal}{A}$ is
responsible for hiding W-type signatures.
Here, $\TyTkg{\lsig}$ packages $\lsig$---recall that $\lsig$ contains the
(self-parameterized) types of all the fields preceding the current
field~$t$---into a dependent tuple type (\ruleref{tyeq/pk/add}).
The term $\seal$ turns a tuple of type $\TyTkg{\lsig}$ into a new tuple of type~$A$
that hides W-type signatures behind $\cU$, if necessary.
%
It is straightforward to find the~$\seal$ that fits the bill, though this process
is not automated in \TT.
In particular, when no hiding is needed, $\seal$ is simply~$x$,
%\EDJ{$\var{0}$ is not identity (substitution), but the first variable, right? Or you meant to say it is identity ``sealing''?}\YZreply{Yes, I meant identity sealing. I cannot say 'sealing' because the paper currently does not use the word sealing anywhere.}\EDJreply{What about just remove the parenthesis and ``the identity''}
and $A$ is $\TyTkg{\lsig}$.
In \cref{fig:stlc-linkage-typing}, $\seal_1$, $\seal_2$, and $\seal_{10}$ are simply $x$,
and $\seal_6$ has the typing
\begingroup
\fontsize{9}{9}\selectfont%
\goodTerm{
  x :
  \big[\texttt{tm} : \TyS{\wcode{\wsig_{\texttt{tm}}}},\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
}{
  \seal_6
}{
  \big[\texttt{tm} : \cU,\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
}.
\endgroup

@@

Derived families can be modeled as linkage transformers inductively
constructed from the introduction forms
$\small\InhId$, $\small\InhExt{h}{\mathit{self}.t}$, $\small\InhOv{h}{\mathit{self}.t}$, %$\small\InhInh{h}$,
etc.
\cref{fig:fmltt-selected} shows the $\beta$-rule of an exemplary transformer,
\ruleref{tmeq/ov/beta}.
It states that applying the transformer $\small\InhOv{h}{\mathit{self}_{\!2}.t_2}$ to
a linkage of form $\LkgAdd{\lkg}{\mathit{self}_{\!1}.t_1}$
overrides the linkage's last field~$t_1$ with~$t_2$.
For instance, the construction below shows that 
$\small\InhOv{\InhId}{\mathit{self}.\wcode{\wsig'_{\texttt{tm}}}}$
is used as the first step in creating a linkage transformer modeling a derived family that
overrides $\wsig_{\texttt{tm}}$ with an extended
signature~$\wsig'_{\texttt{tm}}$:
\vspace{.9ex}
